---
title: "Journal of Information Science"
author: "Billie Anderson"
date: "2023-02-13"
output: html_document
---

This document will provide the R code in the paper entitled "Using R to Develop a Corpus of Full-Text Journal Articles." The authors of this paper are Billie Anderson, Majid Bani-Yaghoub, Vagmi Kantheti, and Scott Curtis. All authors are associated with the University of Missouri Kansas City. Any questions about the code should be directed to Billie Anderson at billie.anderson@umkc.edu.

 
```{r}
library(fulltext)
```

The code in the code chunk below is the code from Figure 2.

```{r}
search_plos <- ft_search(query='spanish flu', from='plos', limit=5000)
search_plos
```

The code in the code chunk below is the code from Figure 3.

```{r}
search_plos <- ft_search(query='spanish flu', from='plos')
search_plos
```

The code in the code chunk below is the code from Figure 4.

```{r}
search_terms <- c('spanish flu','1918-1919 influenza pandemic', '1918-1919 influenza pandemics', 'influenza pandemic, 1918 1919', 'influenza pandemics, 1918-1919','pandemics, 1918-1919 influenza','spanish flu pandemic, 1918-1919', 'spanish flu pandemic, 1918 1919', 'H1N1 influenza pandemic, 1918-1919', 'H1N1 influenza pandemic, 1918-1919')

results_plos <- NULL

for (i in search_terms){
  search_plos <- ft_search(query=i, from='plos', limit=5000)
  
  search_plos_results <- search_plos$plos$data
  
  results_plos <- rbind(results_plos, search_plos_results)
}

```

The code in the code chunk below is the code from Figure 5.

```{r, message=F}
library(tidyverse)

#creating a column, duplicate, that indicates whether the DOI is a duplicate
results_plos$duplicate <- duplicated(results_plos$id)

#filter out the duplicates
unique_results_plos <- filter(results_plos, duplicate == FALSE)
#number of unique DOIs returned 
nrow(unique_results_plos)

#create a character vector object that has the unique DOIs
results_plos_doi_unique <- unique_results_plos$id



```


The code in the code chunk below is the code from Figure 6.

```{r}
#setting the cache path
cache_options_set(full_path="/cloud/project/plos_papers")
#pass the DOIs to ft_get
ft_get(results_plos_doi_unique)

```

The code in the code chunk below is the code from Figure 8.

```{r}
search_crossref <- ft_search(query= 'spanish flu', from='crossref')
search_crossref

search_crossref <- ft_search(query= 'spanish flu', from='crossref', limit=86000)
search_crossref

```


The code in the code chunk below is the code from Figure 9.

```{r}

# first request
opts = list(limit=1000, offset=0)
ft_search(query = 'spanish flu', from = 'crossref', crossrefopts = opts)

# second request
opts = list(limit=1000, offset=1000)
ft_search(query = 'spanish flu', from = 'crossref', crossrefopts = opts)

# and so on

```


The code in the code chunk below is the code from Figure 10.

```{r}

opts=list(limit=1000, offset=0)

ctr=0

for (i in 1:86){
  
  if(i==1){
    opts=list(limit=limit, offset=ctr)
    searchi <- ft_search(query='spanish flu', from='crossref', crossrefopts=opts)
    doisi <- searchi$crossref$data$doi
    assign(paste0("search",i),searchi)
    assign(paste0("dois",i),doisi)
  }
  
  else if(i>1){
    ctr=ctr+1000
     opts=list(limit=limit, offset=ctr)
      searchi <- ft_search(query='spanish flu', from='crossref', crossrefopts=opts)
       doisi <- searchi$crossref$data$doi
       assign(paste0("search",i),searchi)
       assign(paste0("dois",i),doisi)
  }
    
}

```


The code in the code chunk below is the code from Figure 11.

```{r}
#create an option object that contains the API key from Springer
opts <- list(key="<insert key>")
#call the API key using the bmc options argument in ft_search()
search_bmc1 <- ft_search(query = 'spanish flu', from = 'bmc', bmcopts=opts, limit=1000)
search_bmc1

```



